Milestone 2: Core results 01

### 2023-02-11 R_codeP01/reports/MS2_report02.Rmd
elastic net boot and rc

# Models tested
## Lasso
## Post Lasso
## Residuals
## Ridge
## Elastic Net
## Boosting with stumps as base learner
### - mboost
### - xgboost
## PCA feature engineering
## Stacking using different features in the base models 
## Synergistic learning
```{r}
source("/Users/anders/Documents/Master/Cancer/R_codeP01/scripts/90_output01.R")
```

@@

### Mechanistic + Residuals -> proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif)
```
### Mechanistic + Residuals -> proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif)
```
### Mechnaistic + Residuals -> ROR-proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif)
```
### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif)
```

# Summery results: lasso proliferation score (bootstrap) 
```{r}
library(knitr)
data_table <- data.frame(
  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
  cor_mean = c(l_b_6_p$cor_mean, l_b_771_p$cor_mean, l_b_nodes_p$cor_mean, l_b_residuals_771_p_a$cor_mean, l_b_residuals_771_p_m$cor_mean),
  sd_cor = c(l_b_6_p$cor_sd, l_b_771_p$cor_sd, l_b_nodes_p$cor_sd, l_b_residuals_771_p_a$cor_sd, l_b_residuals_771_p_m$cor_sd),
  MSE_mean = c(l_b_6_p$MSE_mean, l_b_771_p$MSE_mean, l_b_nodes_p$MSE_mean, l_b_residuals_771_p_a$MSE_mean, l_b_residuals_771_p_m$MSE_mean),
  MSE_sd = c(l_b_6_p$MSE_sd, l_b_771_p$MSE_sd, l_b_nodes_p$MSE_sd, l_b_residuals_771_p_a$MSE_sd, l_b_residuals_771_p_m$MSE_sd)
)
kable(data_table)
```

# Summery results: lasso ROR+proliferation score (bootstrap) 
```{r}
data_table <- data.frame(
  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
  cor_mean = c(l_b_6_ROR_p$cor_mean, l_b_771_ROR_p$cor_mean, l_b_nodes_ROR_p$cor_mean, l_b_residuals_ROR_p_a$cor_mean, l_b_residuals_ROR_p_m$cor_mean),
  sd_cor = c(l_b_6_ROR_p$cor_sd, l_b_771_ROR_p$cor_sd, l_b_nodes_ROR_p$cor_sd, l_b_residuals_ROR_p_a$cor_sd, l_b_residuals_ROR_p_m$cor_sd),
  MSE_mean = c(l_b_6_ROR_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_b_nodes_ROR_p$MSE_mean, l_b_residuals_ROR_p_a$MSE_mean, l_b_residuals_ROR_p_m$MSE_mean),
  MSE_sd = c(l_b_6_ROR_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_b_nodes_ROR_p$MSE_sd, l_b_residuals_ROR_p_a$MSE_sd, l_b_residuals_ROR_p_m$MSE_sd)
)
kable(data_table)
```

@@

### Mechanistic + Residuals -> proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif)
```
### Mechanistic + Residuals -> proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif.RData")
l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif)
```
### Mechnaistic + Residuals -> ROR-proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif)
```
### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif.RData")
l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif)
```

# Summery results: lasso proliferation score (bootstrap) 
```{r}
library(knitr)
data_table <- data.frame(
  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
  cor_mean = c(l_b_6_p$cor_mean, l_b_771_p$cor_mean, l_b_nodes_p$cor_mean, l_b_residuals_771_p_a$cor_mean, l_b_residuals_771_p_m$cor_mean),
  sd_cor = c(l_b_6_p$cor_sd, l_b_771_p$cor_sd, l_b_nodes_p$cor_sd, l_b_residuals_771_p_a$cor_sd, l_b_residuals_771_p_m$cor_sd),
  MSE_mean = c(l_b_6_p$MSE_mean, l_b_771_p$MSE_mean, l_b_nodes_p$MSE_mean, l_b_residuals_771_p_a$MSE_mean, l_b_residuals_771_p_m$MSE_mean),
  MSE_sd = c(l_b_6_p$MSE_sd, l_b_771_p$MSE_sd, l_b_nodes_p$MSE_sd, l_b_residuals_771_p_a$MSE_sd, l_b_residuals_771_p_m$MSE_sd)
)
kable(data_table)
```

# Summery results: lasso ROR+proliferation score (bootstrap) 
```{r}
data_table <- data.frame(
  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
  cor_mean = c(l_b_6_ROR_p$cor_mean, l_b_771_ROR_p$cor_mean, l_b_nodes_ROR_p$cor_mean, l_b_residuals_ROR_p_a$cor_mean, l_b_residuals_ROR_p_m$cor_mean),
  sd_cor = c(l_b_6_ROR_p$cor_sd, l_b_771_ROR_p$cor_sd, l_b_nodes_ROR_p$cor_sd, l_b_residuals_ROR_p_a$cor_sd, l_b_residuals_ROR_p_m$cor_sd),
  MSE_mean = c(l_b_6_ROR_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_b_nodes_ROR_p$MSE_mean, l_b_residuals_ROR_p_a$MSE_mean, l_b_residuals_ROR_p_m$MSE_mean),
  MSE_sd = c(l_b_6_ROR_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_b_nodes_ROR_p$MSE_sd, l_b_residuals_ROR_p_a$MSE_sd, l_b_residuals_ROR_p_m$MSE_sd)
)
kable(data_table)
```

# Ridge
# Elastic Net
# Boosting with stumps as base learner

>>>>

# Models tested
## Lasso
## Post Lasso
## Residuals
## Ridge
## Elastic Net
## Boosting with stumps as base learner
### - mboost
### - xgboost
## PCA feature engineering
## Stacking using different features in the base models 
## Synergistic learning
```{r}
source("/Users/anders/Documents/Master/Cancer/R_codeP01/scripts/90_output01.R")
source("/Users/anders/Documents/Master/Cancer/R_codeP01/scripts/90_output_ridge_01.R")
```

@@

### Mechanistic + Residuals -> proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_a.RData")
l_b_residuals_771_p_a <- report02_out(lb_obj_residuals_771_prolif_a)
```
### Mechanistic + Residuals -> proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_prolif_m.RData")
l_b_residuals_771_p_m <- report02_out(lb_obj_residuals_771_prolif_m)
```
### Mechnaistic + Residuals -> ROR-proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_a.RData")
l_b_residuals_ROR_p_a <- report02_out(lb_obj_residuals_771_RORprolif_a)
```
### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lb_obj_residuals_771_RORprolif_m.RData")
l_b_residuals_ROR_p_m <- report02_out(lb_obj_residuals_771_RORprolif_m)
```

### Summery results: lasso proliferation score (bootstrap) 
```{r}
library(knitr)
data_table <- data.frame(
  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
  cor_mean = c(l_b_6_p$cor_mean, l_b_771_p$cor_mean, l_b_nodes_p$cor_mean, l_b_residuals_771_p_a$cor_mean, l_b_residuals_771_p_m$cor_mean),
  sd_cor = c(l_b_6_p$cor_sd, l_b_771_p$cor_sd, l_b_nodes_p$cor_sd, l_b_residuals_771_p_a$cor_sd, l_b_residuals_771_p_m$cor_sd),
  MSE_mean = c(l_b_6_p$MSE_mean, l_b_771_p$MSE_mean, l_b_nodes_p$MSE_mean, l_b_residuals_771_p_a$MSE_mean, l_b_residuals_771_p_m$MSE_mean),
  MSE_sd = c(l_b_6_p$MSE_sd, l_b_771_p$MSE_sd, l_b_nodes_p$MSE_sd, l_b_residuals_771_p_a$MSE_sd, l_b_residuals_771_p_m$MSE_sd)
)
kable(data_table)
```

### Summery results: lasso ROR+proliferation score (bootstrap) 
```{r}
data_table <- data.frame(
  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
  cor_mean = c(l_b_6_ROR_p$cor_mean, l_b_771_ROR_p$cor_mean, l_b_nodes_ROR_p$cor_mean, l_b_residuals_ROR_p_a$cor_mean, l_b_residuals_ROR_p_m$cor_mean),
  sd_cor = c(l_b_6_ROR_p$cor_sd, l_b_771_ROR_p$cor_sd, l_b_nodes_ROR_p$cor_sd, l_b_residuals_ROR_p_a$cor_sd, l_b_residuals_ROR_p_m$cor_sd),
  MSE_mean = c(l_b_6_ROR_p$MSE_mean, l_b_771_ROR_p$MSE_mean, l_b_nodes_ROR_p$MSE_mean, l_b_residuals_ROR_p_a$MSE_mean, l_b_residuals_ROR_p_m$MSE_mean),
  MSE_sd = c(l_b_6_ROR_p$MSE_sd, l_b_771_ROR_p$MSE_sd, l_b_nodes_ROR_p$MSE_sd, l_b_residuals_ROR_p_a$MSE_sd, l_b_residuals_ROR_p_m$MSE_sd)
)
kable(data_table)
```

@@

### Mechanistic + Residuals -> proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_a.RData")
l_c_residuals_771_p_a <- report02_out(lc_obj_residuals_771_p_a)
```
### Mechanistic + Residuals -> proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_p_m.RData")
l_c_residuals_771_p_m <- report02_out(lc_obj_residuals_771_p_m)
```
### Mechnaistic + Residuals -> ROR-proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_a.RData")
l_c_residuals_ROR_p_a <- report02_out(lc_obj_residuals_771_ROR_p_a)
```
### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_ROR_p_m.RData")
l_c_residuals_ROR_p_m <- report02_out(lc_obj_residuals_771_ROR_p_m)
```

### Summery results: lasso proliferation score (repeated cross-validation) 
```{r}
library(knitr)
data_table <- data.frame(
  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
  cor_mean = c(l_c_6_p$cor_mean, l_c_771_p$cor_mean, l_c_nodes_p$cor_mean, l_c_residuals_771_p_a$cor_mean, l_c_residuals_771_p_m$cor_mean),
  sd_cor = c(l_c_6_p$cor_sd, l_c_771_p$cor_sd, l_c_nodes_p$cor_sd, l_c_residuals_771_p_a$cor_sd, l_c_residuals_771_p_m$cor_sd),
  MSE_mean = c(l_c_6_p$MSE_mean, l_b_771_p$MSE_mean, l_c_nodes_p$MSE_mean, l_c_residuals_771_p_a$MSE_mean, l_c_residuals_771_p_m$MSE_mean),
  MSE_sd = c(l_c_6_p$MSE_sd, l_c_771_p$MSE_sd, l_c_nodes_p$MSE_sd, l_c_residuals_771_p_a$MSE_sd, l_c_residuals_771_p_m$MSE_sd)
)
kable(data_table)
```

### Summery results: lasso ROR+proliferation score (repeated cross-validation) 
```{r}
data_table <- data.frame(
  Model = c("lasso 6 genes", "lasso 771 genes", "Nodes", "Residual additive", "Residual multiplicative"),
  cor_mean = c(l_c_6_ROR_p$cor_mean, l_c_771_ROR_p$cor_mean, l_c_nodes_ROR_p$cor_mean, l_c_residuals_ROR_p_a$cor_mean, l_c_residuals_ROR_p_m$cor_mean),
  sd_cor = c(l_c_6_ROR_p$cor_sd, l_c_771_ROR_p$cor_sd, l_c_nodes_ROR_p$cor_sd, l_c_residuals_ROR_p_a$cor_sd, l_c_residuals_ROR_p_m$cor_sd),
  MSE_mean = c(l_c_6_ROR_p$MSE_mean, l_c_771_ROR_p$MSE_mean, l_c_nodes_ROR_p$MSE_mean, l_c_residuals_ROR_p_a$MSE_mean, l_c_residuals_ROR_p_m$MSE_mean),
  MSE_sd = c(l_c_6_ROR_p$MSE_sd, l_c_771_ROR_p$MSE_sd, l_c_nodes_ROR_p$MSE_sd, l_c_residuals_ROR_p_a$MSE_sd, l_c_residuals_ROR_p_m$MSE_sd)
)
kable(data_table)
```

# Ridge bootstrap
### 771 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_b_obj_771_p.RData")
r_b_771_p <- report02_out_ridge(r_b_obj_771_p)
```
### 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_b_obj_771_ROR_p.RData")
r_b_771_ROR_p <- report02_out_ridge(r_b_obj_771_ROR_p)
```

# Ridge repeated cross-validation
### 771 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_prolif.RData")
r_c_771_p <- report02_out_ridge(r_c_obj_771_prolif)
```
### 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/r_c_obj_771_RORprolif.RData")
r_c_771_ROR_p <- report02_out_ridge(r_c_obj_771_RORprolif)
```

### Summery results: ridge 771 genes bootstrap and repeated cross-validation
```{r}
data_table <- data.frame(
  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
  cor_mean = c(r_b_771_p$cor_mean, r_b_771_ROR_p$cor_mean, r_c_771_p$cor_mean, r_c_771_ROR_p$cor_mean),
  sd_cor = c(r_b_771_p$cor_sd, r_b_771_ROR_p$cor_sd, r_c_771_p$cor_sd, r_c_771_ROR_p$cor_sd),
  MSE_mean = c(r_b_771_p$MSE_mean, r_b_771_ROR_p$MSE_mean, r_c_771_p$MSE_mean, r_c_771_ROR_p$MSE_mean),
  MSE_sd = c(r_b_771_p$MSE_sd, r_b_771_ROR_p$MSE_sd, r_c_771_p$MSE_sd, r_c_771_ROR_p$MSE_sd)
)
kable(data_table)
```

# Elastic Net - bootstrap
### 771 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_p.RData")
e_b_771_p <- report02_out_ridge(e_b_obj_771_p)
```
### 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_b_obj_771_ROR_p.RData")
e_b_771_ROR_p <- report02_out_ridge(e_b_obj_771_ROR_p)
```

# Elastic Net: cross-validation
### 771 genes -> proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_c_obj_771_prolif.RData")
e_c_771_p <- report02_out_ridge(e_c_obj_771_prolif)
```
### 771 genes -> ROR-proliferation score
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/e_c_obj_771_RORprolif.RData")
e_c_771_ROR_p <- report02_out_ridge(e_c_obj_771_RORprolif)
```

### Summery results: elastic net 771 genes bootstrap and repeated cross-validation
```{r}
data_table <- data.frame(
  Model = c("prolif boot", "ROR-prolif boot", "prolif rep cross-val", "ROR-prolif rep cross-val"),
  cor_mean = c(e_b_771_p$cor_mean, e_b_771_ROR_p$cor_mean, e_c_771_p$cor_mean, e_c_771_ROR_p$cor_mean),
  sd_cor = c(e_b_771_p$cor_sd, e_b_771_ROR_p$cor_sd, e_c_771_p$cor_sd, e_c_771_ROR_p$cor_sd),
  MSE_mean = c(e_b_771_p$MSE_mean, e_b_771_ROR_p$MSE_mean, e_c_771_p$MSE_mean, e_c_771_ROR_p$MSE_mean),
  MSE_sd = c(e_b_771_p$MSE_sd, e_b_771_ROR_p$MSE_sd, e_c_771_p$MSE_sd, e_c_771_ROR_p$MSE_sd)
)
kable(data_table)
```

# Boosting with stumps as base learner
